Revisited hidden weight bit function

### 2024-10-29 RevisedHiddenWeight.tex
Minor changes
Added special case t = n/3

Since $f$ is the sum of a quadratic function and a weightweise affine function, it is a weightwise quadratic function. 
Using the formalism of Definition~\ref{def:wwdegd} $f$ is the WWQ function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
\[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k= \sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]

@@

\begin{proof}
Using Proposition~\ref{prop:restrWT}, the restricted Walsh transform of $f$ can the be written as \[
\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.

@@

\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}
For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$. We then have $p+q+r=n/2$. Consider further the integer polynomial $P_a(z)$ given by the following expression:
\[
P_a(z)=(-z^2+2z+1)^{p}\cdot(-z^2-2z+1)^{q}\cdot(z^2+1)^{r}.
\]

@@

This leads to the following generating function:

\begin{proposition}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$. Denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively. Then the following holds:
    \[
        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
    \]
\end{proposition}

\begin{proof}
    Applying Proposition \ref{proposition:dtn}, we get:
    \begin{align*}
        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.\qedhere
    \end{align*}
\end{proof}

@@

\begin{theorem}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, it holds that:
    \[
        |\wtk{d_{t,n}}{k}(a)|\leq 2^{n-t/2}.
    \]
\end{theorem}

@@

\begin{Corollary}
    For every $a\in\F_2^n$, the following holds:
    \[
        |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{n-t/2}.
    \]
\end{Corollary}

@@

>>>>

Since $f$ is the sum of a quadratic function and a weightweise affine function, it is a weightwise quadratic function. 
Using the formalism of Definition~\ref{def:wwdegd} $f$ is the WWQ function defined by:% $f_0=0$ and for $k\in [1,n]$ $f_k=x_k + \sum_{i=1}^{n/2} (x_i+1) x_{i+n/2}$.
\[f_0=0, \quad \text{ and } \quad \forall k \in [1,n], \, f_k=x_k+\sum_{i=1}^{n/2} (x_i+1) x_{i+\frac{n}{2}}.\]

@@

\begin{proof}
Using Proposition~\ref{prop:restrWT}, the restricted Walsh transform of $f$ can then be written as \[
\wtk{f}{k}(a)=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ c \cdot x}=\Dnka{n}{k}{d},\]
where $d$ is the permutation of $c$ obtained by sending the first $n/2$ elements to the odd positions, and the $n/2$ last ones to the even positions.

@@

\subsection{Study of $\Dnka nka$ through Generating Functions}\label{sec:genfunc}

\begin{definition}\label{defi:P_a}
    For $a\in\F_2^n$, denote by $p=p(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(0,0)$, by $q=q(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})=(1,1)$, and by $r=r(a)$ the number of odd $i\geq 1$ for which $(a_i,a_{i+1})\in\{(0,1),(1,0)\}$. We then have $p+q+r=n/2$. Consider further the integer polynomial $P_a(z)$ given by the following expression:
    \[
    P_a(z)=(-z^2+2z+1)^{p}\cdot(-z^2-2z+1)^{q}\cdot(z^2+1)^{r}.
    \]
\end{definition}

@@

\begin{definition}\label{defi:P_a_t}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Given $a=(b,c)\in\F_2^n$ with $b\in\F_2^{2t}$, denote $n-2t-\w(c)$ and $\w(c)$ by $u$ and $v$, respectively. We  then introduce the following polynomial:
    \[
        P_{a,t}(z)=P_b(z)\cdot(1+z)^u\cdot(1-z)^v.
    \]
\end{definition}

\begin{proposition}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. Let $a\in\F_2^n$. The following holds true: 
    \[
        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k=P_{a,t}(z).
    \]
\end{proposition}

\begin{proof}
    Applying Proposition \ref{proposition:dtn}, we get:
    \begin{align*}
        \sum_{k\in\Z}\wtk{d_{t,n}}{k}(a)z^k&=\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\sum_{k\in\Z}\kraw{k-\ell}{\w(c)}{n-2t}z^{k-\ell}\\
        &=\left(\sum_{\ell=0}^{2t}\Dnka{2t}{\ell}{b}z^\ell\right)\cdot(1+z)^u\cdot(1-z)^v\\
        &=P_b(z)\cdot(1+z)^u\cdot(1-z)^v\\
        &=P_{a,t}(z).\qedhere
    \end{align*}
\end{proof}

@@

\begin{theorem}\label{theorem:bound_D_nka_generalized}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
    \[
        |\wtk{d_{t,n}}{k}(a)|\leq 2^{n-t/2}.
    \]
\end{theorem}

@@

\begin{Corollary}
    Let $t, n\in \N$ with $n$ even and $t\le n/2$. For every $a\in\F_2^n$, the following holds:
    \[
        |\wt{d_{t,n}}(a)|\leq 1+n\cdot 2^{n-t/2}.
    \]
\end{Corollary}

@@

When one is given an explicit value for $t$ in terms of $n$, one can be more careful when employing the proof strategy of Theorem~\ref{theorem:bound_D_nka_generalized}. Let us for instance consider the case $t=n/3$:

\begin{proposition}
    Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
    \[
        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
    \]
\end{proposition}

\begin{proof}
    As before, we want to bound the maximum of $|P_{a,t}(z)|$ on $|z|=1$ for $a\in\F_2^n$, and this will then be an upper bound on $|\wtk{d_{t,n}}{k}(a)|$ for every $k\in[0,n]$. Write $a=(b,c)$ with $b\in\F_2^{2t}$ and let $(p,q,r)=(p(b),q(b),r(b))$, and further consider $u=n-2t-\w(c)$ and $v=\w(c)$ as in Definition~\ref{defi:P_a_t}. Since we want to find a bound of $|P_{a,t}(z)|$ on $|z|=1$ which works for all $a\in\F_2^n$, it makes sense to only consider those $a$ which are actually candidates for maximizing $|P_{a,t}(z)|$, namely those for which only one among $(p,q,r)$ is non-zero, and for which only one among $(u,v)$ is non-zero. This leaves us with the following cases to consider for $(p,q,r;u,v)$:
    \begin{gather*}
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0),\\
         (t,0,0;0,n-2t),\quad(0,t,0;0,n-2t),\quad(0,0,t;0,n-2t).
    \end{gather*}
    Since swapping both $(p,q)$ and $(u,v)$ has the same effect as replacing $z$ by $-z$ in $P_{a,t}(z)$ and therefore does not change the maximum of $|P_{a,t}(z)|$ on $|z|=1$, we can further restrict ourselves to the following tuples for $(p,q,r;u,v)$:
    \[
        (t,0,0;n-2t,0),\quad(0,t,0;n-2t,0),\quad(0,0,t;n-2t,0).
    \]
    Let us for instance find an upper bound of $|P_{a,t}(z)|$ in case $(p,q,r;u,v)=(t,0,0;n-2t,0)$. Since $n-2t=t$ by assumption, we get:
    \[
        P_{a,t}(z)=[(-z^2+2z+1)(1+z)]^t.
    \]
    Writing $z=\cos\alpha+\mathrm i\sin\alpha$, we obtain:
    \[
        |P_{a,t}(z)|^2=[(6-2\cos2\alpha)(2+2\cos\alpha)]^t.
    \]
    Through calculus, one finds that $|(6-2\cos2\alpha)(2+2\cos\alpha)|<2^{9/2}$, and hence that $|P_{a,t}(z)|<2^{9t/4}=2^{3n/4}$. The same upper bound works for the remaining two candidates for $(p,q,r;u,v)$, and we can therefore conclude that $|\wtk{d_{n/3,n}}{k}(a)|\leq 2^{3n/4}$ and that $|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}$.
\end{proof}
